---
title: "p8105_hw5_cev2129"
output: html_document
date: "2024-11-14"
---

```{r}
library(tidyverse)
library(rvest)
set.seed(1)
``` 


**Problem 2**
```{r}
q2_t_test = function(mu, iterations = 5000) { 
  replicate(iterations, {
    data <- rnorm(n = 30, mean = mu, sd = 5)
    t_test <- t.test(data, mu = 0) 
    broom::tidy(t_test)  
  }, simplify = FALSE) |>
    bind_rows() |>
    mutate(mu = mu)
}

values = c(0, 1, 2, 3, 4, 5, 6) 

q2_results = map_dfr(values, q2_t_test) 

q2_power = q2_results |>
  group_by(mu) |>
  summarize(
    mean_estimate = mean(estimate),
    power = mean(p.value < 0.05)
  )

q2_power
```


```{r}
library(ggplot2)
ggplot(q2_power, aes(x = mu, y = power)) + 
  geom_point()
```

Effect size and Power have a positive association. As the true value of mu increases, the difference between the true mu value and the null hypothesized value increases as well, which is known as the effect size. This makes it more feasible to detect a difference, which increases power. This is reflected in the graph above, as the true value of mu increases with power. 


```{r}
null_rejected = q2_results |>
  group_by(mu) |>
  summarize(
    mean_rejected = mean(estimate[p.value < 0.05], na.rm = TRUE)  
  )

q2 = q2_power |>
  left_join(null_rejected, by = "mu")

q2
```

```{r}
plot1 = ggplot(q2, aes(x = mu)) +
  geom_line(aes(y = mean_estimate), color = "red",linetype = "solid") +
  geom_point(aes(y = mean_estimate), color = "red")
plot1

plot2 = plot1 + geom_line(aes(y = mean_rejected), color = "yellow", linetype = "dashed") +
  geom_point(aes(y = mean_rejected), size = 3, color = "yellow") 

plot2
```

The sample average of ðœ‡Ì‚ across tests for which the null is rejected is not approximately equal to the true value of ðœ‡ because of selection bias. The sample average of  ðœ‡Ì‚ for which the null is rejected has selection bias as observations are selected based on the condition that the null was rejected, where this is not the case for the true value of ðœ‡.


**Problem 3**
```{r}
library(dplyr)
library(readr)

homicide_data = read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/refs/heads/master/homicide-data.csv")

homicide_data = homicide_data |>
  mutate(city_state = paste(city, state, sep = ", "))

summary = homicide_data |>
  group_by(city_state) |>
  summarize(
    total = n(),  
    unsolved = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))  
  )
summary
``` 

```{r}
baltimore = homicide_data |>
  filter(city_state == "Baltimore, MD")

prop_test = prop.test(
  x = sum(baltimore[["disposition"]] %in% c("Closed without arrest", "Open/No arrest")), 
  n = nrow(baltimore)) |>
  broom::tidy() 

proportion_estimate = prop_test |>
  pull(estimate) 

conf_interval = prop_test |>
  select(conf.low, conf.high)
```

```{r}
city_prop_tests <- homicide_data |>
  group_by(city_state) |>
  summarise(
    results = list(prop.test(
      x = sum(disposition %in% c("Closed without arrest", "Open/No arrest")),
      n = n()
    ))
  ) |>
  mutate(
    tidy = purrr::map(results, broom::tidy)
  ) |>
  unnest(cols = c(tidy)) |>
  select(city_state, estimate, conf.low, conf.high)
``` 

```{r}
city_plot <- city_prop_tests |>
  arrange(desc(estimate)) |>  
  mutate(city_state = factor(city_state, levels = city_state)) |>  
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point(size = 0.5) +  
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.1) +
  coord_flip() + 
  theme_minimal() + 
  theme(
    axis.text.y = element_text(size = 4))

city_plot  
```
